Sushi monster

### 2025-02-22 inst/sushi.Rmd
name column headings of sushi_table

```{r}
a <- as.matrix(read.table("sushi.txt", skip=22))
set.seed(0)
wanted <- sample(seq_len(nrow(a)),50,replace=TRUE,prob=a[,1])
a <- a[wanted,-1]
```

>>>>

```{r}
a <- as.matrix(read.table("sushi.txt", skip=22))
set.seed(0)
wanted <- sample(seq_len(nrow(a)),50,replace=TRUE,prob=a[,1])
a <- a[wanted,-1]
colnames(a) <- c("first","second","third","fourth","fifth","sixth","seventh","eighth","ninth","tenth")
```
